---
title: "Euromonitor International Coding Task"
author: "Said Maanan"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

## Loading Data

Since the data in the **wimax raw data.csv** file contains too few observations to allow us to confidently perform the analysis, we decided to obtain new data from the ITU website.

```{r}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(prophet)
library(readxl)
library(tidyr)
library(dplyr)
library(readr)
library(purrr)
```

```{r}
ddd_dataset <- read_excel("data/ddd_dataset.xlsx")
wimax <- ddd_dataset[ddd_dataset$`Indicator name`=="Population covered by at least a 4G mobile network (%)",]
```

## Data Cleaning

We will remove excess columns, turn the years into columns, and sort the data by country (alphabetically).

```{r}
wimax <- wimax[order(wimax$Country),]
wimax <- spread(wimax[-c(1553, 1554), c("Country","Year","Value")], Year, value = Value)
```

Many countries have `NA`/`NULL`, therefore I will impute the missing data.

## Data Imputation

I fill the `NA` cells with non-`NA` cells after them.

```{r}
wimax <- wimax %>% 
  pivot_longer(-Country, names_to = "year") %>% 
  mutate(value = value %>% as.numeric()) %>% 
  group_by(Country) %>% 
  fill(value, .direction = "updown") %>% 
  pivot_wider(names_from = year, values_from = value)
```

## Create Datasets

I create the data sets I will use in modelling in the format I need them to be.

```{r}
itu_names <- read_csv("data/itu-emi-countries.csv") %>% 
  rename(Country = `ITU Name`, Cemi = `EMI Name`)

coverage <- read_csv("data/3g data.csv") %>% select(c("CountryName", "Y2012":"Y2020")) %>% 
  rename(Country = CountryName) %>% pivot_longer(-Country, names_to = "ds", values_to = "Expln") %>% 
  mutate(ds = as.Date(gsub("^Y", "", ds), format = "%Y"))

n_data <- wimax %>% 
  left_join(itu_names, by = "Country") %>% 
  mutate(Country = Cemi) %>% select(-Cemi)

wimax <- wimax %>% 
  left_join(itu_names, by = "Country") %>% 
  mutate(Country = Cemi) %>% select(-Cemi) %>% 
  pivot_longer(-Country, names_to = "ds", values_to = "y") %>% 
  mutate(ds = as.Date(ds, format = "%Y")) %>% 
  inner_join(coverage, by = c("Country","ds"))
```

## Modelling

I run the prophet model.

```{r}
make_model = function(df) {
  df$cap <- 100
  m <- prophet(growth = 'logistic')
  m <- add_regressor(m, name = 'Expln')
  m <- fit.prophet(m, df)
  return(m)
}

mdl <- wimax %>% 
  nest(-Country) %>% 
  mutate(model = map(data, make_model)) %>% 
  ungroup()

```

## Forecasting

I make forecasts, plots and save them.

```{r}

expln <- read_csv("data/3g data.csv") %>% select(c("CountryName", "Y2012":"Y2030")) %>% 
  pivot_longer(-CountryName, names_to = "ds", values_to = "Expln") %>%
  mutate(ds = as.Date(gsub("^Y", "", ds), format = "%Y")) %>%
  rename(Country = CountryName)

make_frcst = function(m, df) {
  future <- make_future_dataframe(m, 10, freq = 'year', include_history = TRUE)
  future$Expln <- df$Expln
  future$cap <- 100
  fcst <- predict(m, future)
  return(fcst)
}

frs <- expln %>% 
  nest(-Country) %>% 
  rename(pred_data = data) %>% 
  inner_join(mdl, by = "Country") %>% 
  mutate(prediction = map2(model, pred_data, make_frcst)) %>% 
  mutate(plot = map2(model, prediction, plot)) %>% 
  ungroup()
```

## Display Forecasts

I iteratively plot the figures.

```{r}
plots <- map2(frs$plot, frs$Country, ~(.x + labs(title = .y)))

for (plot in plots) {
  print(plot)
  cat('\n\n')
}
```

## Put Results in CSV File

First we gather the data we want.

```{r}

extradat <- read_csv("data/3g data.csv") %>% select(c("CountryName":"Unit"))

unnested <- unnest(frs, prediction) %>% 
  mutate(Year = year(ds), Pred = yhat) %>% select(Country, Year, Pred) %>% 
  spread(Year, value = Pred) %>% select("Country", "2021":"2030") %>% 
  left_join(extradat, by = c("Country" = "CountryName"), all.x = TRUE) %>% 
  left_join(n_data, by = "Country", all.x = TRUE) %>% 
  select("Country","CountryCode":"2020","2021":"2030")

```

We need to remove the data that is unwanted.

```{r}

exceptions <- read_csv("data/WiMAX exceptions.csv") %>% 
  filter(!row_number() %in% c(10, 14)) %>% 
  select(c(1,3)) %>% mutate(Years = gsub('Y','', Years))

Count <- exceptions$CountryName
Year  <- exceptions$Years

for (i in seq_along(Count)) {
  unnested[unnested$Country == Count[i], ][[Year[i]]] <- NA
}

unnested
```

We can now save the data.

```{r}
write.csv(unnested, "result.csv", row.names = FALSE)
```